\noindent
{\textbf{\Huge Abstract}}
\vspace{1cm}

This graduation project presents the design, development, and deployment of a non-invasive, AI-driven blood glucose level estimation system utilizing smartphone Photoplethysmography (PPG) signals. Traditional methods for metabolic tracking rely heavily on invasive, painful, and costly finger-prick glucometers, which often lead to low patient compliance and fragmented longitudinal tracking. By transforming consumer-grade smartphones into decentralized medical diagnostic tools, this work eliminates the physical and financial barriers associated with continuous glycemic monitoring.

The proposed framework introduces an optimized, lightweight 1D-ResNet architecture engineered specifically for real-time inference on resource-constrained mobile devices. To overcome the persistent challenge of clinical data scarcity inherent in biomedical signal processing, cross-domain Transfer Learning was successfully leveraged. This paradigm enables the deep learning model to accurately encapsulate the complex, non-linear dynamics of capillary micro-circulation and optical arterial pulses directly from raw, full-frame remote PPG (rPPG) streams without human intervention or manual feature engineering.

The entire methodology is integrated into a production-ready mobile application featuring a localized real-time PPG signal acquisition pipeline, adaptive signal quality estimators to filter somatic noise, and a minimalist biomedical UI/UX configuration. The successful end-to-end execution validates that the system achieves high predictive accuracy with a significantly reduced computational footprint (low FLOPs and parameter density). This research establishes a scalable, painless, and highly accessible consumer health paradigm for modern proactive diabetes management and decentralized clinical analytics.