\clearpage
\thispagestyle{empty}

\noindent
{\textbf{\Huge Acknowledgment}}
\vspace{1cm}

All praise is due to ALLAH, the Almighty, our Lord and Sustainer. It is only by His grace, mercy, and divine guidance that we were able to successfully navigate this academic journey and bring this graduation project to fruition.

We would like to express our deepest gratitude to our primary supervisor, \textbf{Prof. Osama Omar}, for his invaluable vision, academic leadership, and continuous endorsement throughout the lifecycle of this project.

We are profoundly grateful to \textbf{Dr. Mohammed Abdelnasser} and \textbf{Dr. Ahmed Nor} for their exceptional mentorship, rigorous technical insights, and for providing the critical analytical advice that substantially shaped our research methodology and engineering execution.

Special thanks and appreciation are extended to our former teaching assistant, \textbf{Eng. Abdelrahman Yahia}, for his dedicated hands-on guidance and initial technical contributions prior to his transition to another academic institution. We are equally grateful to \textbf{Eng. Somaya Abdelkhier} for stepping in, embracing the project framework, and providing the critical domain expertise and continuous support necessary to bridge our theoretical models with practical implementation.

Finally, we would like to express our heartfelt gratitude to our parents and families for their unconditional love, continuous sacrifices, and unwavering encouragement over the past years. Without their monumental support, completing our engineering studies would have been impossible.